Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-29 pldi14/sec-practice.tex
Patch up discussion of "real" list changes, and nits

Two important lessons from the evaluations are:
\begin{itemize}
\item As anticipated in \cref{ssec:self-maint}, to achieve good performance our current
  implementation requires some form of dead code elimination, such as laziness.
%Either laziness or dead-code elimination is required for
%good performance ().
\item Incrementalization increases code size significantly.
  Analyzing and addressing this increase is left for future work.
\end{itemize}

>>>>

An important lessons from the evaluations is that,
as anticipated in \cref{ssec:self-maint}, to achieve good
performance our current implementation requires some form of dead
code elimination, such as laziness.
% %Either laziness or dead-code elimination is required for
% %good performance ().
